Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
Nope, need to keep reindexing notation distinct from composition otherwise things get confusing.

Of interest here is the Grothendieck construction for $\Func{-}{\cat{C}}: \Set^{\op} \to \Cat$, the indexed
category which sends any set $X$ to the category of $X$-indexed families $\Func{X}{\cat{C}}$ and any function
$f: X \to Y$ to the reindexing functor $- \comp f: \Func{Y}{\cat{C}} \to \Func{X}{\cat{C}}$ .

>>>>

Of interest to us is the Grothendieck construction for $\Func{-}{\cat{C}}: \Set^{\op} \to \Cat$, the indexed
category which sends any set $X$ to the category of $X$-indexed families $\Func{X}{\cat{C}}$ and any function
$f: X \to Y$ to the reindexing functor $\reindex{-}{f}: \Func{Y}{\cat{C}} \to \Func{X}{\cat{C}}$ .
